\documentclass[11pt, a4paper]{resume}
\usepackage[top=0.25in,left=0.3in,right=0.3in,bottom=0.6in,scale=0.9]{geometry} % Document margins
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{lipsum}
\usepackage{array}
\usepackage{linegoal}

\hypersetup{
    colorlinks=true,
    linkcolor=purple,
    filecolor=magenta,      
    urlcolor=cyan,
}
% \renewcommand{\familydefault}{\sfdefault} %sans-serif everywhere

\definecolor{mypurple}{HTML}{794BC4}
\definecolor{gray}{HTML}{727272}
\definecolor{othergray}{HTML}{808080}
\newcommand{\important}[1]{
	\textcolor{mypurple}{#1}
}
\newcommand{\greyed}[1]{
	\textcolor{gray}{#1}
}
\newcommand{\titleX}[1]{
	\begin{LARGE}
    	\important{\centerline{\textbf{#1}}}
    \end{LARGE}
}

\newcommand{\fillit}[1]{
	\leavevmode\xleaders\hbox{#1}\hfill\kern0pt
}

\newcommand{\sectionTitle}[1]{
	\begin{Large}
    	\important{\textbf{#1}} 
    \end{Large}
    \important{\rlap{\rule[.5ex]{\linegoal}{0.5pt}}{}}
%     \important{\underline{{\hspace{\textwidth}}}}
%     \fillit{\important{\rule{0.5cm}{0.4cm}}}
     \vspace{0.1em}\\
%     \important{\noindent\rule{17cm}{0.4pt}} \newline
}

\newcommand{\sectionSubtitleX}[1]{
	\begin{large}
    \important{#1}
    \end{large}
    \fillit{\important{.}}
}

\newcommand{\textbox}[1]{
  \parbox{.333\textwidth}{#1}
}

\newenvironment{Jobsection}[3]{ % 3 input arguments - company name,  job title and duration
\noindent\textbox{\bf #1\hfill}\textbox{\hfil #2\hfil}\textbox{\hfill #3}
  \begin{list}{$\bullet$}{\leftmargin=1em} % \bullet used for bullets, no indentation
   \itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
  }{
  \end{list}
  \vspace{0.2em} % Some space after the list of bullet points
}

\newcommand{\education}[3]{ % 3 input arguments - company name,  job title and duration
\noindent\parbox{.3\textwidth}{\bf #1\hfill}\parbox{.45\textwidth}{\hfil #2\hfil}\parbox{.25\textwidth}{\hfill #3}
}


\setlength{\parindent}{0pt}
\thispagestyle{empty} % no page numbers
\begin{document}
\titleX{Kaustubh Hiware}
\normalsize
% 150, Ulhas Nagar, Manewada Square, Nagpur, India 
\vspace{6pt}
\greyed{\centerline{\faEnvelopeO \, \href{mailto:hiwarekaustubh@gmail.com}{ hiwarekaustubh@gmail.com} \, $\bullet$ \,\faMobile\, +91 86683\, 92709 \, $\bullet$ \,\faGithub / \faLinkedin \, \href{https://github.com/kaustubhhiware}{KaustubhHiware} \,  $\bullet$ \, \faGlobe \, \href{https://kaustubhhiware.in}{KaustubhHiware.in}}}

\vspace{-2em}
\sectionTitle{Work Experience}
\begin{Jobsection}{\href{https://stride.ai}{Stride.AI, Bangalore}}{NLP Intern}{ Jul $^{\prime}$19 - Sep$^{\prime}$19}
% \item Used and deployed probablistic models to extract useful entities from unstructured data using NLP.
\item Developed Information Extraction pipelines for Proof of Concepts to achieve Robotic Process Automation.
\item Currently developing an automated Question Answer Generation (Natural Language Understanding) platform.
\end{Jobsection}

\begin{Jobsection}{\href{https://drive.google.com/file/d/1EcfIC_g8bx3whaxMdOkFyZx4TCqA1RAq/view?usp=sharing}{Schlumberger, Pune Tech Center}}{Software Intern}{ May $^{\prime}$18 - Jun$^{\prime}$18}
\item Developed {\bf RESTful backend API} in C\#, .NET that provided endpoints to existing computation engine.
\item Wrote a DLS-compliant {\bf frontend in Angular}, which was used by multiple field experts from South-east Asia.
\item Rewarded a {\bf Pre-Placement Offer} as Software Engineer for diligent contribution to the organisation.
\end{Jobsection}

% \begin{Jobsection}{\href{https://drive.google.com/file/d/0B5iU6cWw36rOVWZIcllPY3RSd2c/view?usp=sharing}{Elanic, Bangalore}}{Backend developer Intern}{ May $^{\prime}$17 - Jun$^{\prime}$17}
% \item Built complete CRUD for 2 classes, in NodeJS REST API. Abstraction written extended to {\bf 50\%} of all classes.
% \item Developed a npm module \href{https://www.npmjs.com/package/urlparamify}{urlparamify} to be used in website, which received over {\bf 3000} downloads so far.
% \end{Jobsection}
% -----------------------------------

\sectionTitle{Education\vspace{0.5em}}
\education{Indian Institute of Technology,\\ Kharagpur}{\centerline{Bachelor's \& Master's of Technology} \centerline{in Computer Science \& Engineering}}{Apr $^{\prime}$14 - Jun $^{\prime}$ 19 \\\hspace*{\fill} CGPA: 8.47/10}
% \vspace{0.05em}\\
% \education{Shivaji Science College, Nagpur}{Higher Secondary School Education, 2014}{95.54\%\,(99.98\%ile)}\\
% \education{Sandipani School, Nagpur}{Secondary School Education, CBSE, 2012}{96.8\%}

\sectionSubtitleX{Projects}

\begin{rSubsection}{SAVITR: A System for Real-time Location Extraction from Microblogs during Emergencies.}{Jul $^{\prime}$17 - Apr $^{\prime}$19}{Research Project under Asst. Prof. Saptarshi Ghosh}{\hspace*{\fill} CSE Dept., IIT Kharagpur}
\item Developed a {\bf pre-warning system} to detect potential disaster situations: \href{http://savitr.herokuapp.com}{savitr.herokuapp.com} and identified geospatial distribution and situational importance of tweets. A paper was accepted at \href{https://www.cse.iitk.ac.in/users/kripa/smerp2018/}{SMERP - WWW'18}.
% \item Helps identify geospatial distribution of important tweets and classifying tweets as situational and non-situational, which can help in disaster relief and mitigation. A paper on the same was accepted at \href{https://www.cse.iitk.ac.in/users/kripa/smerp2018/}{SMERP - WWW'18}.
\item Further developed a {\bf disaster-relief assistant} that identifies and matches resources collected from social media. Secured first place in Microsoft's \href{https://drive.google.com/open?id=1bcVOIePJl6ahP0JRqtrUgSZdXo2LQaLb}{Codefundo++'19}, Kharagpur. Amongst top 21 teams out of 5400 participants.
\end{rSubsection}


\begin{rSubsection}{Deep Learning in Legal Data Analytics}{July $^{\prime}$18 - Apr $^{\prime}$19}{Masters' Thesis Project under Prof. Saptarshi Ghosh}{\hspace*{\fill} CSE Dept., IIT Kharagpur}
\item Utilizing legal knowledge to deploy a \textbf{search engine} with thematic segmentation.
\item Analyzed summarization for legal documents and reported findings in a research paper at \href{http://ecir2019.org}{ECIR.}
% \item Aim to build a {\bf knowledge graph} for Indian court cases. A paper has been accepted in \href{http://ecir2019.org/}{ECIR 2019} (reproducibility). 
% \item The deliverables are a {\bf search system} for legal experts and a {\bf chatbot} for legal advice by historic cases lookup.
\end{rSubsection}

\begin{rSubsection}{Emotion detection using Smart Devices}{Jul $^{\prime}$17 - Apr$^{\prime}$18}{Bachelors' Thesis Project under Prof. Bivas Mitra \& Prof. Niloy Ganguly}{\hspace*{\fill} CSE Dept., IIT Kharagpur}
\item Investigated the role of touch interactions in {\bf multi-state emotion detection}. Involves jointly modeling typing features and  user provided self-reports to build a {\bf personalized machine learning model}. Obtained an accuracy of {\bf 73\%}.
\item 2 research publications accepted - at \href{https://iui.acm.org/2019/}{IUI}  and \href{https://www.journals.elsevier.com/international-journal-of-human-computer-studies}{IJHCS journal}. %  \href{https://recsys.acm.org/recsys18/}{RecSys} and \href{http://www.ieeesmc.org/publications/transactions-on-human-machine-systems}{THMS} journal.
\end{rSubsection}


% \begin{rSubsection}{Understanding code-mixing patterns in celebrity tweets}{Apr $^{\prime}$17}{Academic Project under Prof. Pabitra Mitra}{\hspace*{\fill} CSE Dept., IIT Kharagpur}
% \item Used Louvain algorithm to detect communities in large networks with scala and t-SNE in python.
% \item Reached a maximum modularity of 98.6\%. Open sourced the project on \href{https://github.com/kaustubhhiware/Graphwise}{Github}.
% \end{rSubsection}

\begin{rSubsection}{Core CS projects \& self projects}{}{}{}
\item Implemented a crash tolerant, multi-threaded collaborative download system as a \href{https://github.com/kaustubhhiware/swift}{Distributed Systems} project.
% \item Implemented a queue based scheduler, memory management and signal handling for \href{https://github.com/kaustubhhiware/OSLab}{pintOS prototype}.
% \item Implemented a \href{https://github.com/kaustubhhiware/cOMPILER}{restricted grammar C compiler} made using flex,yacc and gnu assembler.\\
\item Hobby projects, available on \href{https://github.com/kaustubhhiware}{GitHub} - a \href{https://github.com/kaustubhhiware/ NotiFyre}{terminal notifier},an\,\href{https://github.com/kaustubhhiware/c0derunR}{ NLP-powered IDE}, a\,\href{https://github.com/kaustubhhiware/Foodspark}{food-ordering portal} and a\,\href{https://github.com/kaustubhhiware/facebook-archive}{facebook data analysis toolkit} amongst others.\  More here: \href{https://kaustubhhiware.in/#projects}{kaustubhhiware.in/\#projects}.
\end{rSubsection}

\sectionSubtitleX{Coursework} 
\begin{tabular}{>{\footnotesize}c>{\footnotesize}c>{\footnotesize}c>{\footnotesize}c>{\footnotesize}c}
Deep Learning$^+$ & Machine Learning & Natural Language Processing$^+$ & Image Processing$^+$ & Artificial Intelligence \\
Data Analytics$^+$ & Social Computing$^+$ & Database Management Systems$^+$ & Computer Networks$^+$ & Software Engineering$^+$ \\
Compilers$^+$ & Algorithms 1$^+$ \& 2 & Distributed Systems$^+$ & Operating Systems$^+$ & {\scriptsize \,[$^+$ \,\,Practicum included]} \\
\end{tabular}\\
% -----------------------------------

\sectionTitle{Technical skills}
$\bullet$ Programming Languages: Python,\,\, C/C++,\,\, Javascript/NodeJS \,\, (Proficient)\,\, $\|$ C\#,\,\, Java,\,\, Scala,\,\, R\,\, (Familiar) \\
$\bullet$ Web : HTML,\,\,  CSS/SCSS,\,\,  Bootstrap,\,\,  Jekyll,\,\,  Django,\,\,  React,\,\,  Angular \\
$\bullet$  Frameworks/Tools
: Postman,\, Spark,\, MongoDB,\, Git,\, Shell,\, Elasticsearch,\, Heroku,\, LaTeX,\, Markdown\,
% -----------------------------------

\sectionTitle{Extra-curricular}
$\bullet$ Received Honorable Mention for contribution in Tech by IITKGP Gymkhana (Awarded to 10 students of 2000).\\
$\bullet$ Secured \href{https://sites.nyuad.nyu.edu/hackathon/}{Second Place} in NYU Abu Dhabi's International Hackathon on Social Good.\\
$\bullet$ {\bf Maintainer, \href{http://metakgp.github.io}{MetaKGP}}: Conduct various activities to promote hacker culture and collaboration on campus.\\
$\bullet$ Mentored a team of 20 to secure \href{}{Silver} in Inter Hall OpenSoft competition, IIT Kharagpur.\\
$\bullet$ {\bf Mentor}: Guided freshers towards open source, in \href{https://kwoc.kossiitkgp.in/}{Kharagpur WoC},  \href{https://gssoc.tech/projects.html#facebook-archive}{GirlScript SoC} and  \href{https://drive.google.com/open?id=1b1xN6dxnPMP9vKaUW6zxeE__70iP1AgJ}{Google code-in}. \\


% $\bullet$ \textbf{5} Research papers published - at \, \href{https://www2018.thewebconf.org/proceedings/#wrk-131}{SMERP - WWW'18} \,,\, \href{https://sites.google.com/site/textgraphs2017/program}{ACL TextGraphs'17} \,,\, \href{https://ecir2019.org/accepted-papers/#reproducibilitypapers}{ECIR 2019} \,\&\, \href{https://iui.acm.org/2019/acceptedpapers.html#shortpapers}{IUI'19}. \\
% $\bullet$ {\bf Speaker} at \href{https://www.youtube.com/watch?v=lk4ciY3NSbA}{Kshitij IIT Kharagpur's Open Source Summit, 2018} and \href{https://twitter.com/IIITAPragma/status/1085833015995953152}{Pragma, IIIT Allahabad, 2019}\\
% $\bullet$ {\bf Teaching Assistant}: for Machine Learning (Autumn 2018) and Principles of Programming Languages (Spring 2019). \\
% $\bullet$ Presented posters at \href{https://web.northeastern.edu/sds/ICNDE2018/}{ICNDE, 2018} and 7th Inter IIT Tech Meet, 2018. \\
%$\bullet$ Shortlisted for \href{https://drive.google.com/open?id=0B5iU6cWw36rOamZLWHZENWdlY0k}{Smart India Hackathon'17}, \href{https://www.aicte-india.org/sites/default/files/Shortlisted and waitlisted Teams indo singapore hackathon 2018.pdf}{Indo-Singapore Hackathon'18}.
% \, Also a \href{https://drive.google.com/file/d/0B5iU6cWw36rOc0gzcjZPRTd5SkU/view?usp=sharing}{mentor} to 6 junior students to guide them in non-academic pursuits.
% -----------------------------------
	\vspace*{\fill}
    \vspace{-1.2em}
	\begin{flushright}
    % \scriptsize
	\tiny \textcolor{othergray}{Last updated: Aug 15, 2019.}
	\end{flushright}
    
\end{document}
