%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
% 
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
% 
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
% 
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
% Important notes:
% This template needs to be compiled with XeLaTeX.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

\documentclass[a4paper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\newcommand{\onepage}[1]{
  \ifdefined\onep
  #1
  \fi
}
\newcommand{\experience}[3]{
  \descriptnonewline{#1} \hfill \textit{#2} \\
  \location{#3}
}

\newcommand{\experiencetwo}[2]{
  \descriptnonewline{#1} \hfill \textit{#2} \\
}

\newcommand{\newlink}[2]{
  \href{#1}{\color{black}#2}
}

\begin{document}
\namesection{Kaustubh}{Hiware}{
  Computer Science and Engineering, IIT Kharagpur \\
  \href{https://cse.iitkgp.ac.in/~hknarendra/}{cse.iitkgp.ac.in/~hknarendra} \\
  \href{mailto:hiwarekaustubh@iitkgp.ac.in}{ hiwarekaustubh@iitkgp.ac.in}  |  (+91) 8768829567\\
  C-123,Azad Hall of Residence, Indian Institute of Technology Kharagpur - 721302, India}
\begin{minipage}[t]{0.30\textwidth} % The left column takes up 33% of the text width of the page

  \section{Education} 

  \descriptbig{IIT Kharagpur}

  \descript{B.Tech+M.Tech in \\Computer Science and Engineering}
  \location{2014-2019(expected) \\ CGPA: \textit{8.19/10}}

  \sectionspace
  \sectionspace
  
  \descriptbig{Shivaji Science College, \\ Nagpur(State Board)}
  \descript{Senior Secondary Grade 12 (99.98 percentile)}
  \location{Overall: \textbf{95.54\%}}

  \sectionspace
  \sectionspace
  
  \descriptbig{Sandipani School, \\ Nagpur (CBSE)}
  \descript{Secondary Grade 10}
  \location{Overall: \textbf{96.8\%}}    
  
  \sectionspace

  \section{CS Coursework}
  Machine Learning, Deep Learning*,
  Social Computing,
  Artificial Intelligence, 
  Natural Language Processing,
  Algorithms$^+$, Data Analytics,
  Software Engineering$^+$, Database Management$^+$,
  Networks$^+$, Compilers$^+$, Operating Systems$^+$  \\

  {\footnotesize \textit{\textbf{(* denotes ongoing courses, \\$^+$ denotes lab included) }}} \\

  \sectionspace

  \section{Skills}

  \runsubsection{}
  \descriptbig{Programming Languages}
  C/C++ \textbullet{} Python \textbullet{} Java \\
  \textbullet{} Javascript/NodeJS \\
  \textbullet{} Assembly \textbullet{} Scala \textbullet{} R

  \sectionspace
  \sectionspace

  \descriptbig{Web}
  HTML \textbullet{} CSS/SCSS \textbullet{} Django \\
  \textbullet{} Jekyll \textbullet{} Bootstrap \textbullet{} React

  \sectionspace
  \sectionspace

  \descriptbig{Utilities \& Frameworks}
  Git \textbullet{} Shell/Fish \textbullet{} MySQL\\
  \textbullet{} Elasticsearch \textbullet{} TravisCI \\
  \textbullet{} MongoDB \textbullet{} \LaTeX\\
  \textbullet{} Heroku
  
\end{minipage}
\hfill
\begin{minipage}[t]{0.69\textwidth}% total only upto 0.99

  \section{Work Experience}
  \runsubsection{}
  \experience{\href{https://drive.google.com/open?id=0B5iU6cWw36rOVWZIcllPY3RSd2c}{Developer Intern}}{May '17 - Jun '17}{Elanic, Bangalore}
  \vspace{\topsep}
  \begin{tightitemize}
  \item Worked on feature addition, automating test suite, data sanitization, indexing and writing abstractions on the backend.
  \item	Developed a npm module \href{https://www.npmjs.com/package/urlparamify}{\textbf{urlparamify}} to be used in developing website, which received over \href{https://drive.google.com/open?id=0B5iU6cWw36rOd09Bc3ZNV1p4UTQ}{\bf{2500}} downloads in a month.
  \end{tightitemize}
%  \sectionspace
%
%  \runsubsection{}
%  \experience{\href{https://github.com/orgs/coala/teams/coala-developers/members?&query=kaustubh}{Open source Developer}}{March '17 - Present}{coala: Language Independent Code Analysis}
%  \begin{tightitemize}
%  \item coala provides a unified command-line interface for linting and fixing code, independent of programming languages used.
%  \item	Sucessfully merged 4 out of 6 submitted patches.
%  \end{tightitemize}
  
  \section{Projects}

  \runsubsection{}
  \experience{Emotion detection using smart devices}{Jan '17-Present}{B.Tech project, IIT Kharagpur}
  \begin{tightitemize}
  	\item Identify emotional state cues from smart device usage patterns.
  	\item Build a ML based model with minimal user interaction.
  \end{tightitemize}
  \sectionspace

  \runsubsection{}
  \experience{Transductive learning for Derivational Morphology}{}{IIT Kharagpur}
  \begin{tightitemize}
  	\item A Graph based semi-supervised approach for analysis of Derivational Nouns in Sanskrit.
  	\item Worked under the supervision of Prof. Pawan Goyal and \href{http://www.cnergres.iitkgp.ac.in/}{CNeRG}.
  	\item \href{https://scholar.google.co.in/citations?view_op=view_citation&hl=en&user=9iIiFjMAAAAJ&citation_for_view=9iIiFjMAAAAJ:u5HHmVD_uO8C}{\bf{Research paper}} accepted in ACL TextGraphs 2017.
  \end{tightitemize}
  \sectionspace

  \runsubsection{}
  \experience{Graphwise - Distributed Graph Processing}{Apr '17}{IIT Kharagpur}
  \begin{tightitemize}
  	\item Used Louvain algorithm to detect communities in large networks in scala and t-SNE for dimensionality reduced data visualisation.
  	\item Reached a maxium modularity of \textbf{98.6\%}. \newlink{https://github.com/kaustubhhiware/Graphwise}{\bold{Github repository}}.

  \end{tightitemize}
  \sectionspace

  \runsubsection{}
  \experience{Foodspark}{Feb '17}{IIT Kharagpur}
  \begin{tightitemize}
  	\item A Django webapp for online food ordering system.
  	\item Fully functional website sans payment hosted \newlink{http://foodkgp.pythonanywhere.com/}{\bold{here}}.
  \end{tightitemize}
  \sectionspace
 
  \runsubsection{}
  \experience{c0derunR}{Jan '17}{\href{https://drive.google.com/open?id=0B5iU6cWw36rOOG9yZ2hxSTFTUEk}{Microsoft Code.fun.do 2017}}
  \begin{tightitemize}
  	\item An Integrated Development Environment webapp build using HackerEarth API. \newlink{http://c0derunr.herokuapp.com/}{\bf{Hosted website}}.
  	\item Includes a static website generator reflecting on-the-go changes.
  \end{tightitemize}
  \sectionspace

  \runsubsection{}
  \experiencetwo{Notifyre}{Dec '16}
  \begin{tightitemize}
	\item A terminal task notifier with support of basic customzations. 
	\item Supports bash, zsh and fish shell. \newlink{https://github.com/kaustubhhiware/NotiFyre}{\bold{Github repository}}.
  \end{tightitemize}
  \sectionspace
  
%  \runsubsection{}
%  \experience{Tiny-C compiler}{Nov '16}{IIT Kharagpur}
%  \begin{tightitemize}
%  	\item A restricted grammar C compiler made using flex,yacc and gnu assembler. Available on  \href{https://github.com/kaustubhhiware/cOMPILER}{GitHub}.
%  	\item A Compilers course project under Prof. Partha Pratim Das, IIT Kharagpur.
%  \end{tightitemize}
%  \sectionspace

%  \runsubsection{}
%  \experiencetwo{Wordabulary}{May '16}
%  \begin{tightitemize}
%    \item A python pip module for grammar statistics. Available on \newlink{https://github.com/kaustubhhiware/Wordabulary}{GitHub}.
%    \item Support trivial document analysis. Developed as a module to validate Zipf's law.
%  \end{tightitemize}
%  \sectionspace

%  \runsubsection{}
%  \experience{Data extraction from a 2-D plot}{Feb '16-Mar '16}{OpenSoft competition, IIT Kharagpur}
%  \begin{tightitemize}
%  	\item Created a module to extract graph information from a plot and create the corresponding data table using OpenCV libraries and Tesseract.
%  	\item The code for the same is available at \newlink{https://github.com/Azad-Hall/open-soft-2015-2016}{Github}.
%  \end{tightitemize}
%  \sectionspace

%  \runsubsection{}
%  \experience{Department Information System}{Mar '16}{Software Project}
%  \begin{tightitemize}
%  	\item Created a software which allows the administrator to perform managerial tasks. Source code on \newlink{https://github.com/kaustubhhiware/DepInfosys}{Github}.
%  	\item Software project(Java) under Prof. Partha Pratim Das, IIT Kharagpur .
%  \end{tightitemize}
%  \sectionspace
 
  \section{Awards and Achievements}

\fontspec[Path = fonts/raleway/]{Raleway-Light}\fontsize{11pt}{11pt}\selectfont {

  \begin{tabular}{rll}
  	2017     & Proposal \href{https://docs.google.com/presentation/d/1ndJbIQCxFEf__I55yOOME-a_UGWDv1KMlukVE2lbDeA/}{\bf{ResSearch}} selected for final round of \href{https://drive.google.com/open?id=0B5iU6cWw36rOamZLWHZENWdlY0k}{\bf{Smart India Hackathon}}. \\
    2014	 & \bold{All India Rank 1874}, JEE Advanced, among 150,000 candidates\\
    2014	 & \bold{All India Rank 277}, JEE Mains(I), among 1.5 million candidates\\
    2014     & \bold{All India Rank 22}, JEE Mains(II), among 150,000 candidates\\
    2011     & \bold{Maharashtra Talent Search}(Govt of Maharashtra)scholarship recipient\\
  \end{tabular}
}\\
\normalfont

  \sectionspace
  \section{Miscellaneous}
  \vspace{\topsep}
  \begin{tightitemize}
  	\item Frequent open source contributor on \href{https://github.com/kaustubhhiware}{\bold{GitHub}.}
  	\item \newlink{https://github.com/orgs/coala/teams/coala-developers/members?&query=kaustubh}{\bf{Open source developer}} for coala, a language agnostic code analysis tool.
  	\item Software trainee, Autonomous Ground Vehicle, for Mar '15 - Nov '15.
  	\item Participated in Open IIT Data Analytics, 2015.
  \end{tightitemize}

  \sectionspace

\end{minipage}

	% \vspace*{\fill}
	\begin{flushright}
	\footnotesize Last updated on 15 Aug '17
	\end{flushright}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% TeX-engine: xetex
%%% End: