\documentclass[11pt, a4paper]{resume}
\usepackage{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{fontawesome}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{lipsum}
\hypersetup{
    colorlinks=true,
    linkcolor=purple,
    filecolor=magenta,      
    urlcolor=cyan,
}
% \renewcommand{\familydefault}{\sfdefault} %sans-serif everywhere

\definecolor{mypurple}{HTML}{794BC4}
\definecolor{gray}{HTML}{727272}
\newcommand{\important}[1]{
	\textcolor{mypurple}{#1}
}
\newcommand{\greyed}[1]{
	\textcolor{gray}{#1}
}
\newcommand{\titleX}[1]{
	\begin{LARGE}
    	\important{\centerline{\textbf{#1}}}
    \end{LARGE}
}

\newcommand{\sectionTitle}[1]{
	\begin{Large}
    	\important{\textbf{#1}}\newline
    \end{Large}
    \important{\noindent\rule{19cm}{0.4pt}} \newline
}

\newcommand\textbox[1]{
  \parbox{.333\textwidth}{#1}
}

\newenvironment{Jobsection}[3]{ % 3 input arguments - company name,  job title and duration
\noindent\textbox{\bf #1\hfill}\textbox{\hfil #2\hfil}\textbox{\hfill #3}
  \begin{list}{$\bullet$}{\leftmargin=1em} % \bullet used for bullets, no indentation
   \itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
  }{
  \end{list}
  \vspace{0.5em} % Some space after the list of bullet points
}



\setlength{\parindent}{0pt}
\thispagestyle{empty} % no page numbers
\begin{document}
\titleX{Kaustubh Hiware}
\normalsize
% 150, Ulhas Nagar, Manewada Square, Nagpur, India 
\vspace{6pt}
\greyed{\centerline{\faEnvelopeO \, \href{mailto:hiwarekaustubh@iitkgp.ac.in}{ 
hiwarekaustubh@iitkgp.ac.in} \, $\bullet$ \,\faMobile\, +91 87688\, 29567\, $\bullet$ \, 
\faTwitter \, \href{https://twitter.com/kaustubhhiware}{@KaustubhHiware} \, $\bullet$ \, 
\faGithub \, \href{https://github.com/kaustubhhiware}{@KaustubhHiware}
}}

\vspace{2pt}
\sectionTitle{Education}
\begin{Jobsection}{Indian Institute of Technology,\\ Kharagpur}{Bachelor's \& Master's of 
Technology \centerline{in Computer Science \& Engineering}}{Apr $^{\prime}$14 - Jun 
$^{\prime}$ 19 (expected) \\\hspace*{\fill} CGPA: 8.29/10}
\item
\end{Jobsection}

\begin{Jobsection}{Sandipani School, Nagpur}{Higher Secondary School Education}{2012}
\item Overall CGPA: 10/10
\item Represented school at multiple city-level debates, extempores and quizzes.
\item Held student position for 3 yrs - As House vice-captain, then Deputy Head Boy and as 
Head Boy.
\end{Jobsection}
% -----------------------------------


\sectionTitle{Technical skills}
$\bullet$ Programming Languages: Python,\, C/C++,\, Javascript/NodeJS \, (Proficient)\, $\|$ 
C\#,\, Java,\, Scala,\, R\, (Familiar) \\
$\bullet$ Web : HTML, CSS/SCSS, Bootstrap, Jekyll, Django, React, Angular \\
$\bullet$  Frameworks/Tools
: OpenCV, Postman, Spark, MongoDB, Git, Shell, Elasticsearch, Heroku, LATEX, Markdown
% -----------------------------------

\sectionTitle{Work Experience}
\begin{Jobsection}{Schlumberger, Pune Tech Center}{Software Intern}{ May $^{\prime}$18 - 
Jun$^{\prime}$18}
\item Developed {\bf RESTful backend API} in C\#, .NET that provided endpoints to existing 
computation engine.
\item Wrote a DLS-compliant {\bf frontend in AngularJS}, which was tested  by multiple field 
experts from India and Malaysia.
\item Rewarded a {\bf Pre-Placement Offer} as Software Engineer for diligent contribution to 
the organisation.
\end{Jobsection}

\begin{Jobsection}{Schlumberger, Pune Technology Center}{Software Intern}{ May $^{\prime}$18 
- Jun$^{\prime}$18}
\item Developed RESTful backend API from scratch in C\#, .NET that provided endpoints to 
existing computation engine.
\item Wrote a DLS-compliant frontend in AngularJS, which was tested  by multiple field 
experts from India and Malaysia.
\item Rewarded a Pre-Placement Offer as Software Engineer for diligent contribution to the 
organisation.
\end{Jobsection}
% -----------------------------------

\sectionTitle{Additional skills}
% -----------------------------------

\end{document}

